The Linguistic Landscape of Stream-of-Consciousness Literature

### 2024-04-03 paper/paper.qmd
update formatting

---
title: "The Linguistic Landscape of Stream-of-Consciousness Literature"
subtitle: "Exploring Word Frequency and Mental Health Themes in the Works of Joyce, Woolf, Proust, Mansfield and Eliot from Project Gutenberg"
author: Quang Mai
thanks: "Code and data are available at: https://github.com/ponolite/stream-consciousness-language.git"
date: today
date-format: long
abstract: "This project focuses on understanding the language used by renowned, transnational stream of consciousness authors James Joyce, Virginia Woolf, Marcel Proust, Katherine Mansfield and T.S Eliot. By analyzing the word frequency of their famous works, I explore mental health themes like anxiety, depression, trauma, and existential angst. Through word frequency analysis of nine novels, I aim to uncover shared linguistic patterns and gain insights into the authors' mental states, offering a glimpse into themes of self-identity and existential contemplation."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@@

@@

@@

@@

## Gendered Mental Landscape of Stream of Consciousness Novels

@@

## Combined Texts: Trends, Word Networks, Bigram and Trigram Analsis

>>>>

---
title: "The Linguistic Landscape of Stream-of-Consciousness Literature"
subtitle: "Exploring Word Frequency and Mental Health Themes in the Works of Joyce, Woolf, Proust, Mansfield and Eliot from Project Gutenberg"
author: Quang Mai
thanks: "Code and data are available at: https://github.com/ponolite/stream-consciousness-language.git"
date: today
date-format: long
abstract: "This project focuses on understanding the language used by renowned, transnational stream of consciousness authors James Joyce, Virginia Woolf, Marcel Proust, Katherine Mansfield and T.S Eliot. By analyzing the word frequency of their famous works, I explore mental health themes like anxiety, depression, trauma, and existential angst. Through word frequency analysis of nine novels, I aim to uncover shared linguistic patterns and gain insights into the authors' mental states, offering a glimpse into themes of self-identity and existential contemplation."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

We expect a negative relationship between average household income and the number of children per child care space by ward. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

```
\newpage

@@

```
\newpage
## Gendered Mental Landscape of Stream of Consciousness Novels

@@

\newpage
## Combined Texts: Trends, Word Networks, Bigram and Trigram Analsis
